---
title: "expanding_shinyapp"
output: html_document
date: "2023-06-16"
---

```{r}
library(tidyverse)
library(pdftools)
library(shiny)
source("pdf_function_full.R")
pdf_function_full("STAT113_Fall_2020_1.pdf")
source("meta_function.R")
meta_function("STAT113_Fall_2020_1.pdf")
source("sb_function.R")
sb_function("STAT113_Fall_2020_1.pdf")
library(knitr)
library(pander)
# install.packages("shadowtext")
library(shadowtext)
```

adding static perc heatmap
```{r}
ui <- fluidPage( 
  titlePanel("Upload File Here"),
  sidebarLayout(
    sidebarPanel(
      fileInput('file_input', 'Upload Student Evaluation
                File (.pdf format only)',
                accept = c('pdf'))),
    mainPanel(
      uiOutput("pdfview"), 
      plotOutput("heatmap"),
      plotOutput("heatmap_perc")
    ))
)
server <- function(input, output, session) {
  output$pdfview <- renderTable({
    req(input$file_input)
    pdf_df <- pdf_function_full(input$file_input$datapath)
    pdf_df <- pdf_df |> filter(responses_hm != "Too High" &
                        responses_hm != "Too Low" &
                        responses_hm != "Appropriate" &
                        responses_hm != "Somewhat High" &
                        responses_hm != "Somewhat Low")
    pdf_display <- pdf_df |>
      select(responses, n_students, perc, univ_perc, full_question) |>
      rename(Responses = 'responses',
             Count = 'n_students',
             Percent_of_Students = 'perc',
             University_Percent = 'univ_perc',
             Question = 'full_question')
    return(head(pdf_display))
  })
  output$heatmap <- renderPlot({
    req(input$file_input)
    pdf_df <- pdf_function_full(input$file_input$datapath)
    pdf_df <- pdf_df |> filter(responses_hm != "Too High" &
                        responses_hm != "Too Low" &
                        responses_hm != "Appropriate" &
                        responses_hm != "Somewhat High" &
                        responses_hm != "Somewhat Low")
    pdf_df <- pdf_df |> mutate(question_2 = 
                       fct_relevel(full_question, c("Valuable",
                                               "Organized",
                                               "Learning",
                                               "Fair",
                                               "Timely",
                                               "Constructive",
                                               "Rec_Prof",
                                               "Rec_Course",
                                               "Effective")))
    meta_df <- meta_function(input$file_input$datapath)
    title <- paste(meta_df[1, 2], meta_df[1, 1], sep = " ", collapse = NULL)
    subtitle <- paste(meta_df[1, 3], meta_df[1, 4], sep = " ", collapse = NULL)
    ggplot(data = pdf_df, aes(x = responses_hm, y = fct_rev(question_2),
                                fill = count_hm)) +
    geom_tile() +
    scale_fill_viridis_c(direction = 1) +
      labs(x = "Responses",
           y = "Questions",
           fill = "Count",
           title = title,
           subtitle = subtitle) +
  geom_text(aes(label = count_hm,
                fontface = 'bold',
                size = 20),
            show.legend = FALSE) +
      theme_bw() +
  theme(plot.title = element_text(hjust = 0.5,
                                  size = 18),
        plot.subtitle = element_text(hjust = 0.5),
        legend.box.background = element_rect(colour = "black"),
        axis.text = element_text(size = 14),
        axis.title = element_text(size = 16),
        legend.title = element_text(size = 13),
        legend.text = element_text(size = 9)) 
  })
  output$heatmap_perc <- renderPlot({
    req(input$file_input)
    pdf_df <- pdf_function_full(input$file_input$datapath)
    pdf_df <- pdf_df |> filter(responses_hm != "Too High" &
                        responses_hm != "Too Low" &
                        responses_hm != "Appropriate" &
                        responses_hm != "Somewhat High" &
                        responses_hm != "Somewhat Low")
    pdf_df <- pdf_df |> mutate(question_2 = 
                       fct_relevel(full_question, c("Valuable",
                                               "Organized",
                                               "Learning",
                                               "Fair",
                                               "Timely",
                                               "Constructive",
                                               "Rec_Prof",
                                               "Rec_Course",
                                               "Effective")))
    pdf_df <- pdf_df |> mutate(perc = as.double(perc))
    meta_df <- meta_function(input$file_input$datapath)
    title <- paste(meta_df[1, 2], meta_df[1, 1], sep = " ", collapse = NULL)
    subtitle <- paste(meta_df[1, 3], meta_df[1, 4], sep = " ", collapse = NULL)
    ggplot(data = pdf_df, aes(x = responses_hm, y = fct_rev(question_2),
                                fill = perc)) +
    geom_tile() +
    scale_fill_viridis_c(direction = 1) +
      labs(x = "Responses",
           y = "Questions",
           fill = "Percent",
           title = title,
           subtitle = subtitle) +
      geom_text(aes(label = perc,
                  fontface = 'bold',
                  size = 20),
            show.legend = FALSE) +
      theme_bw() +
      theme(plot.title = element_text(hjust = 0.5,
                                  size = 18),
            plot.subtitle = element_text(hjust = 0.5),
            legend.box.background = element_rect(colour = "black"),
            axis.text = element_text(size = 14),
            axis.title = element_text(size = 16),
            legend.title = element_text(size = 13),
            legend.text = element_text(size = 9)) 
  })
}
shinyApp(ui, server)
```

adding summary output table, replacing other table 
```{r}
ui <- fluidPage( 
  titlePanel("Upload File Here"),
  sidebarLayout(
    sidebarPanel(
      fileInput('file_input', 'Upload Student Evaluation
                File (.pdf format only)',
                accept = c('pdf'))),
    mainPanel(
      plotOutput("heatmap"),
      plotOutput("heatmap_perc"),
      uiOutput("pdfview")
    ))
)
server <- function(input, output, session) {
  output$heatmap <- renderPlot({
    req(input$file_input)
    pdf_df <- pdf_function_full(input$file_input$datapath)
    pdf_df <- pdf_df |> filter(responses_hm != "Too High" &
                        responses_hm != "Too Low" &
                        responses_hm != "Appropriate" &
                        responses_hm != "Somewhat High" &
                        responses_hm != "Somewhat Low")
    pdf_df <- pdf_df |> mutate(question_2 = 
                       fct_relevel(full_question, c("Valuable",
                                               "Organized",
                                               "Learning",
                                               "Fair",
                                               "Timely",
                                               "Constructive",
                                               "Rec_Prof",
                                               "Rec_Course",
                                               "Effective")))
    meta_df <- meta_function(input$file_input$datapath)
    title <- paste(meta_df[1, 2], meta_df[1, 1], sep = " ", collapse = NULL)
    subtitle <- paste(meta_df[1, 3], meta_df[1, 4], sep = " ", collapse = NULL)
    ggplot(data = pdf_df, aes(x = responses_hm, y = fct_rev(question_2),
                                fill = count_hm)) +
    geom_tile() +
    scale_fill_viridis_c(direction = 1) +
      labs(x = "Responses",
           y = "Questions",
           fill = "Count",
           title = title,
           subtitle = subtitle) +
  geom_text(aes(label = count_hm,
                fontface = 'bold',
                size = 20),
            show.legend = FALSE) +
      theme_bw() +
  theme(plot.title = element_text(hjust = 0.5,
                                  size = 18),
        plot.subtitle = element_text(hjust = 0.5),
        legend.box.background = element_rect(colour = "black"),
        axis.text = element_text(size = 14),
        axis.title = element_text(size = 16),
        legend.title = element_text(size = 13),
        legend.text = element_text(size = 9)) 
  })
  output$heatmap_perc <- renderPlot({
    req(input$file_input)
    pdf_df <- pdf_function_full(input$file_input$datapath)
    pdf_df <- pdf_df |> filter(responses_hm != "Too High" &
                        responses_hm != "Too Low" &
                        responses_hm != "Appropriate" &
                        responses_hm != "Somewhat High" &
                        responses_hm != "Somewhat Low")
    pdf_df <- pdf_df |> mutate(question_2 = 
                       fct_relevel(full_question, c("Valuable",
                                               "Organized",
                                               "Learning",
                                               "Fair",
                                               "Timely",
                                               "Constructive",
                                               "Rec_Prof",
                                               "Rec_Course",
                                               "Effective")))
    pdf_df <- pdf_df |> mutate(perc = as.double(perc))
    meta_df <- meta_function(input$file_input$datapath)
    title <- paste(meta_df[1, 2], meta_df[1, 1], sep = " ", collapse = NULL)
    subtitle <- paste(meta_df[1, 3], meta_df[1, 4], sep = " ", collapse = NULL)
    ggplot(data = pdf_df, aes(x = responses_hm, y = fct_rev(question_2),
                                fill = perc)) +
    geom_tile() +
    scale_fill_viridis_c(direction = 1) +
      labs(x = "Responses",
           y = "Questions",
           fill = "Percent",
           title = title,
           subtitle = subtitle) +
      geom_text(aes(label = perc,
                  fontface = 'bold',
                  size = 20),
            show.legend = FALSE) +
      theme_bw() +
      theme(plot.title = element_text(hjust = 0.5,
                                  size = 18),
            plot.subtitle = element_text(hjust = 0.5),
            legend.box.background = element_rect(colour = "black"),
            axis.text = element_text(size = 14),
            axis.title = element_text(size = 16),
            legend.title = element_text(size = 13),
            legend.text = element_text(size = 9)) 
  })
  output$pdfview <- renderTable({
    req(input$file_input)
    meta_df <- meta_function(input$file_input$datapath)
    meta_df <- meta_df |> rename(Course_Number = 'course_num',
                                 Subject = 'subject',
                                 Semester = 'semester',
                                 Year = 'year',
                                 Control_Number = 'control_num',
                                 Total_Evals = 'n_evals',
                                 Total_Evals_University = 'n_evals_univ')
    return(meta_df)
  })
}
shinyApp(ui, server)
```

add button for counts v perc 
```{r}
ui <- fluidPage( 
  titlePanel("Upload File Here"),
  sidebarLayout(
    sidebarPanel(
      fileInput('file_input', 'Upload Student Evaluation
                File (.pdf format only)',
                accept = c('pdf')),
      radioButtons(inputId = "choose", label = "Counts or Percents of Students",
                   choices = c("count_hm", "perc")),
      ),
    mainPanel(
      plotOutput("heatmap"),
      plotOutput("heatmap_perc"),
      uiOutput("pdfview")
    ))
)
server <- function(input, output, session) {
  output$heatmap <- renderPlot({
    req(input$file_input)
    pdf_df <- pdf_function_full(input$file_input$datapath)
    pdf_df <- pdf_df |> filter(responses_hm != "Too High" &
                        responses_hm != "Too Low" &
                        responses_hm != "Appropriate" &
                        responses_hm != "Somewhat High" &
                        responses_hm != "Somewhat Low")
    pdf_df <- pdf_df |> mutate(question_2 = 
                       fct_relevel(full_question, c("Valuable",
                                               "Organized",
                                               "Learning",
                                               "Fair",
                                               "Timely",
                                               "Constructive",
                                               "Rec_Prof",
                                               "Rec_Course",
                                               "Effective")))
    meta_df <- meta_function(input$file_input$datapath)
    title <- paste(meta_df[1, 2], meta_df[1, 1], sep = " ", collapse = NULL)
    subtitle <- paste(meta_df[1, 3], meta_df[1, 4], sep = " ", collapse = NULL)
    ggplot(data = pdf_df, aes(x = responses_hm, y = fct_rev(question_2),
                                fill = count_hm)) +
    geom_tile() +
    scale_fill_viridis_c(direction = 1) +
      labs(x = "Responses",
           y = "Questions",
           fill = "Count",
           title = title,
           subtitle = subtitle) +
  geom_text(aes(label = count_hm,
                fontface = 'bold',
                size = 20),
            show.legend = FALSE) +
      theme_bw() +
  theme(plot.title = element_text(hjust = 0.5,
                                  size = 18),
        plot.subtitle = element_text(hjust = 0.5),
        legend.box.background = element_rect(colour = "black"),
        axis.text = element_text(size = 14),
        axis.title = element_text(size = 16),
        legend.title = element_text(size = 13),
        legend.text = element_text(size = 9)) 
  })
  output$heatmap_perc <- renderPlot({
    req(input$file_input)
    pdf_df <- pdf_function_full(input$file_input$datapath)
    pdf_df <- pdf_df |> filter(responses_hm != "Too High" &
                        responses_hm != "Too Low" &
                        responses_hm != "Appropriate" &
                        responses_hm != "Somewhat High" &
                        responses_hm != "Somewhat Low")
    pdf_df <- pdf_df |> mutate(question_2 = 
                       fct_relevel(full_question, c("Valuable",
                                               "Organized",
                                               "Learning",
                                               "Fair",
                                               "Timely",
                                               "Constructive",
                                               "Rec_Prof",
                                               "Rec_Course",
                                               "Effective")))
    pdf_df <- pdf_df |> mutate(perc = as.double(perc))
    meta_df <- meta_function(input$file_input$datapath)
    title <- paste(meta_df[1, 2], meta_df[1, 1], sep = " ", collapse = NULL)
    subtitle <- paste(meta_df[1, 3], meta_df[1, 4], sep = " ", collapse = NULL)
    ggplot(data = pdf_df, aes(x = responses_hm, y = fct_rev(question_2),
                                fill = perc)) +
    geom_tile() +
    scale_fill_viridis_c(direction = 1) +
      labs(x = "Responses",
           y = "Questions",
           fill = "Percent",
           title = title,
           subtitle = subtitle) +
      geom_text(aes(label = perc,
                  fontface = 'bold',
                  size = 20),
            show.legend = FALSE) +
      theme_bw() +
      theme(plot.title = element_text(hjust = 0.5,
                                  size = 18),
            plot.subtitle = element_text(hjust = 0.5),
            legend.box.background = element_rect(colour = "black"),
            axis.text = element_text(size = 14),
            axis.title = element_text(size = 16),
            legend.title = element_text(size = 13),
            legend.text = element_text(size = 9)) 
  })
  output$pdfview <- renderTable({
    req(input$file_input)
    meta_df <- meta_function(input$file_input$datapath)
    meta_df <- meta_df |> rename(Course_Number = 'course_num',
                                 Subject = 'subject',
                                 Semester = 'semester',
                                 Year = 'year',
                                 Control_Number = 'control_num',
                                 Total_Evals = 'n_evals',
                                 Total_Evals_University = 'n_evals_univ')
    return(meta_df)
  })
}
shinyApp(ui, server)
```

making buttons work 
```{r}
ui <- fluidPage( 
  titlePanel("Upload File Here"),
  sidebarLayout(
    sidebarPanel(
      fileInput('file_input', 'Upload Student Evaluation
                File (.pdf format only)',
                accept = c('pdf')),
      radioButtons(inputId = "choose", label = "Counts or Percents of Students",
                   choices = c("count_hm", "perc")),
      ),
    mainPanel(
      plotOutput("heatmap"),
      uiOutput("pdfview")
    ))
)
server <- function(input, output, session) {
  output$heatmap <- renderPlot({
    req(input$file_input)
    pdf_df <- pdf_function_full(input$file_input$datapath)
    pdf_df <- pdf_df |> filter(responses_hm != "Too High" &
                        responses_hm != "Too Low" &
                        responses_hm != "Appropriate" &
                        responses_hm != "Somewhat High" &
                        responses_hm != "Somewhat Low")
    pdf_df <- pdf_df |> mutate(question_2 = 
                       fct_relevel(full_question, c("Valuable",
                                               "Organized",
                                               "Learning",
                                               "Fair",
                                               "Timely",
                                               "Constructive",
                                               "Rec_Prof",
                                               "Rec_Course",
                                               "Effective")))
    pdf_df <- pdf_df |> mutate(perc = as.double(perc))
    meta_df <- meta_function(input$file_input$datapath)
    title <- paste(meta_df[1, 2], meta_df[1, 1], sep = " ", collapse = NULL)
    subtitle <- paste(meta_df[1, 3], meta_df[1, 4], sep = " ", collapse = NULL)
    ggplot(data = pdf_df, aes(x = responses_hm, y = fct_rev(question_2),
                                fill = .data[[input$choose]])) +
    geom_tile() +
    scale_fill_viridis_c(direction = 1) +
      labs(x = "Responses",
           y = "Questions",
           fill = input$choose,
           title = title,
           subtitle = subtitle) +
      geom_text(aes(label = .data[[input$choose]],
                  fontface = 'bold',
                  size = 20),
            show.legend = FALSE) +
      theme_bw() +
      theme(plot.title = element_text(hjust = 0.5,
                                  size = 18),
            plot.subtitle = element_text(hjust = 0.5),
            legend.box.background = element_rect(colour = "black"),
            axis.text = element_text(size = 14),
            axis.title = element_text(size = 16),
            legend.title = element_text(size = 13),
            legend.text = element_text(size = 9)) 
  })
  output$pdfview <- renderTable({
    req(input$file_input)
    meta_df <- meta_function(input$file_input$datapath)
    meta_df <- meta_df |> rename(Course_Number = 'course_num',
                                 Subject = 'subject',
                                 Semester = 'semester',
                                 Year = 'year',
                                 Control_Number = 'control_num',
                                 Total_Evals = 'n_evals',
                                 Total_Evals_University = 'n_evals_univ')
    return(meta_df)
  })
}
shinyApp(ui, server)
```

adding table to double check labels 
```{r}
ui <- fluidPage( 
  titlePanel("Upload File Here"),
  sidebarLayout(
    sidebarPanel(
      fileInput('file_input', 'Upload Student Evaluation
                File (.pdf format only)',
                accept = c('pdf')),
      radioButtons(inputId = "choose", label = "Counts or Percents of Students",
                   choices = c("count_hm", "perc")),
      ),
    mainPanel(
      plotOutput("heatmap"),
      uiOutput("pdfview"),
      uiOutput("pdf_display")
    ))
)
server <- function(input, output, session) {
  output$heatmap <- renderPlot({
    req(input$file_input)
    pdf_df <- pdf_function_full(input$file_input$datapath)
    pdf_df <- pdf_df |> filter(responses_hm != "Too High" &
                        responses_hm != "Too Low" &
                        responses_hm != "Appropriate" &
                        responses_hm != "Somewhat High" &
                        responses_hm != "Somewhat Low")
    pdf_df <- pdf_df |> mutate(question_2 = 
                       fct_relevel(full_question, c("Valuable",
                                               "Organized",
                                               "Learning",
                                               "Fair",
                                               "Timely",
                                               "Constructive",
                                               "Rec_Prof",
                                               "Rec_Course",
                                               "Effective")))
    pdf_df <- pdf_df |> mutate(perc = as.double(perc))
    meta_df <- meta_function(input$file_input$datapath)
    title <- paste(meta_df[1, 2], meta_df[1, 1], sep = " ", collapse = NULL)
    subtitle <- paste(meta_df[1, 3], meta_df[1, 4], sep = " ", collapse = NULL)
    ggplot(data = pdf_df, aes(x = responses_hm, y = fct_rev(question_2),
                                fill = .data[[input$choose]])) +
    geom_tile() +
    scale_fill_viridis_c(direction = 1) +
      labs(x = "Responses",
           y = "Questions",
           fill = input$choose,
           title = title,
           subtitle = subtitle) +
      geom_text(aes(label = .data[[input$choose]],
                  fontface = 'bold',
                  size = 20),
            show.legend = FALSE) +
      theme_bw() +
      theme(plot.title = element_text(hjust = 0.5,
                                  size = 18),
            plot.subtitle = element_text(hjust = 0.5),
            legend.box.background = element_rect(colour = "black"),
            axis.text = element_text(size = 14),
            axis.title = element_text(size = 16),
            legend.title = element_text(size = 13),
            legend.text = element_text(size = 9)) 
  })
  output$pdfview <- renderTable({
    req(input$file_input)
    meta_df <- meta_function(input$file_input$datapath)
    meta_df <- meta_df |> rename(Course_Number = 'course_num',
                                 Subject = 'subject',
                                 Semester = 'semester',
                                 Year = 'year',
                                 Control_Number = 'control_num',
                                 Total_Evals = 'n_evals',
                                 Total_Evals_University = 'n_evals_univ')
    return(meta_df)
  })
  output$pdf_display <- renderTable({
    req(input$file_input)
    pdf_df <- pdf_function_full(input$file_input$datapath)
    pdf_df <- pdf_df |> filter(responses_hm != "Too High" &
                        responses_hm != "Too Low" &
                        responses_hm != "Appropriate" &
                        responses_hm != "Somewhat High" &
                        responses_hm != "Somewhat Low")
    pdf_display <- pdf_df |>
      select(responses, n_students, perc, univ_perc, full_question) |>
      rename(Responses = 'responses',
             Count = 'n_students',
             Percent_of_Students = 'perc',
             University_Percent = 'univ_perc',
             Question = 'full_question')
    return(head(pdf_display))
  })
}
shinyApp(ui, server)
```

rename buttons for count or percent 
```{r}
ui <- fluidPage( 
  titlePanel("Upload File Here"),
  sidebarLayout(
    sidebarPanel(
      fileInput('file_input', 'Upload Student Evaluation
                File (.pdf format only)',
                accept = c('pdf')),
      radioButtons(inputId = "choose", label = "Counts or Percent of Students",
                   choices = c("Count", "Percent")),
      ),
    mainPanel(
      plotOutput("heatmap", width = "100%"),
      uiOutput("pdfview"),
      uiOutput("pdf_display")
    ))
)
server <- function(input, output, session) {
  output$heatmap <- renderPlot({
    req(input$file_input)
    pdf_df <- pdf_function_full(input$file_input$datapath)
    pdf_df <- pdf_df |> filter(responses_hm != "Too High" &
                        responses_hm != "Too Low" &
                        responses_hm != "Appropriate" &
                        responses_hm != "Somewhat High" &
                        responses_hm != "Somewhat Low")
    pdf_df <- pdf_df |> mutate(question_2 = 
                       fct_relevel(full_question, c("Valuable",
                                               "Organized",
                                               "Learning",
                                               "Fair",
                                               "Timely",
                                               "Constructive",
                                               "Rec_Prof",
                                               "Rec_Course",
                                               "Effective")))
    pdf_df <- pdf_df |> mutate(perc = as.double(perc))
    pdf_df <- pdf_df |> rename(Count = 'count_hm',
                               Percent = 'perc')
    meta_df <- meta_function(input$file_input$datapath)
    title <- paste(meta_df[1, 2], meta_df[1, 1], sep = " ", collapse = NULL)
    subtitle <- paste(meta_df[1, 3], meta_df[1, 4], sep = " ", collapse = NULL)
    ggplot(data = pdf_df, aes(x = responses_hm, y = fct_rev(question_2),
                                fill = .data[[input$choose]])) +
    geom_tile() +
    scale_fill_viridis_c(direction = 1) +
      labs(x = "Responses",
           y = "Questions",
           fill = input$choose,
           title = title,
           subtitle = subtitle) +
      geom_text(aes(label = .data[[input$choose]],
                  fontface = 'bold',
                  size = 20),
            show.legend = FALSE) +
      theme_bw() +
      theme(plot.title = element_text(hjust = 0.5,
                                  size = 18),
            plot.subtitle = element_text(hjust = 0.5),
            legend.box.background = element_rect(colour = "black"),
            axis.text = element_text(size = 14),
            axis.title = element_text(size = 16),
            legend.title = element_text(size = 13,
                                        hjust = 0.5),
            legend.text = element_text(size = 10,
                                       hjust = 0.5)) 
  }, height = 400, width = 900)
  output$pdfview <- renderTable({
    req(input$file_input)
    meta_df <- meta_function(input$file_input$datapath)
    meta_df <- meta_df |> rename(Course_Number = 'course_num',
                                 Subject = 'subject',
                                 Semester = 'semester',
                                 Year = 'year',
                                 Control_Number = 'control_num',
                                 Total_Evals = 'n_evals',
                                 Total_Evals_University = 'n_evals_univ')
    return(meta_df)
  })
  output$pdf_display <- renderTable({
    req(input$file_input)
    pdf_df <- pdf_function_full(input$file_input$datapath)
    pdf_df <- pdf_df |> filter(responses_hm != "Too High" &
                        responses_hm != "Too Low" &
                        responses_hm != "Appropriate" &
                        responses_hm != "Somewhat High" &
                        responses_hm != "Somewhat Low")
    pdf_display <- pdf_df |>
      select(responses, n_students, perc, univ_perc, full_question) |>
      rename(Responses = 'responses',
             Count = 'n_students',
             Percent_of_Students = 'perc',
             University_Percent = 'univ_perc',
             Question = 'full_question')
    return(head(pdf_display))
  })
}
shinyApp(ui, server)
```

trying to add static faceted bar graph
```{r}
ui <- fluidPage( 
  titlePanel("Upload File Here"),
  sidebarLayout(
    sidebarPanel(
      fileInput('file_input', 'Upload Student Evaluation
                File (.pdf format only)',
                accept = c('pdf')),
      radioButtons(inputId = "choose", label = "Counts or Percent of Students",
                   choices = c("Count", "Percent")),
      ),
    mainPanel(
      plotOutput("heatmap", width = "100%"),
      plotOutput("bar_graph", width = "100%"), 
      uiOutput("pdfview"),
      uiOutput("pdf_display")
    ))
)
server <- function(input, output, session) {
  output$heatmap <- renderPlot({
    req(input$file_input)
    pdf_df <- pdf_function_full(input$file_input$datapath)
    pdf_df <- pdf_df |> filter(responses_hm != "Too High" &
                        responses_hm != "Too Low" &
                        responses_hm != "Appropriate" &
                        responses_hm != "Somewhat High" &
                        responses_hm != "Somewhat Low")
    pdf_df <- pdf_df |> mutate(question_2 = 
                       fct_relevel(full_question, c("Valuable",
                                               "Organized",
                                               "Learning",
                                               "Fair",
                                               "Timely",
                                               "Constructive",
                                               "Rec_Prof",
                                               "Rec_Course",
                                               "Effective")))
    pdf_df <- pdf_df |> mutate(perc = as.double(perc))
    pdf_df <- pdf_df |> rename(Count = 'count_hm',
                               Percent = 'perc')
    meta_df <- meta_function(input$file_input$datapath)
    title <- paste(meta_df[1, 2], meta_df[1, 1], sep = " ", collapse = NULL)
    subtitle <- paste(meta_df[1, 3], meta_df[1, 4], sep = " ", collapse = NULL)
    ggplot(data = pdf_df, aes(x = responses_hm, y = fct_rev(question_2),
                                fill = .data[[input$choose]])) +
    geom_tile() +
    scale_fill_viridis_c(direction = 1) +
      labs(x = "Responses",
           y = "Questions",
           fill = input$choose,
           title = title,
           subtitle = subtitle) +
      geom_text(aes(label = .data[[input$choose]],
                  fontface = 'bold',
                  size = 20),
            show.legend = FALSE) +
      theme_bw() +
      theme(plot.title = element_text(hjust = 0.5,
                                  size = 18),
            plot.subtitle = element_text(hjust = 0.5),
            legend.box.background = element_rect(colour = "black"),
            axis.text = element_text(size = 14),
            axis.title = element_text(size = 16),
            legend.title = element_text(size = 13,
                                        hjust = 0.5),
            legend.text = element_text(size = 10,
                                       hjust = 0.5)) 
  }, height = 400, width = 900)
  output$bar_graph <- renderPlot({
    req(input$file_input)
    pdf_df <- pdf_function_full(input$file_input$datapath)
    pdf_df <- pdf_df |> filter(responses_hm != "Too High" &
                        responses_hm != "Too Low" &
                        responses_hm != "Appropriate" &
                        responses_hm != "Somewhat High" &
                        responses_hm != "Somewhat Low")
    pdf_df <- pdf_df |> mutate(question_2 = 
                       fct_relevel(full_question, c("Valuable",
                                               "Organized",
                                               "Learning",
                                               "Fair",
                                               "Timely",
                                               "Constructive",
                                               "Rec_Prof",
                                               "Rec_Course",
                                               "Effective")))
    pdf_df <- pdf_df |> mutate(perc = as.double(perc))
    pdf_df <- pdf_df |> rename(Count = 'count_hm',
                               Percent = 'perc')
    meta_df <- meta_function(input$file_input$datapath)
    title <- paste(meta_df[1, 2], meta_df[1, 1], sep = " ", collapse = NULL)
    subtitle <- paste(meta_df[1, 3], meta_df[1, 4], sep = " ", collapse = NULL)
    ggplot(data = pdf_df, aes(x = responses_hm, y = .data[[input$choose]])) +
      geom_col(aes(fill = .data[[input$choose]])) +
      facet_wrap(~question_2) +
      labs(x = "Responses",
           y = input$choose,
           title = title,
           subtitle = subtitle) +
      scale_fill_viridis_c() +
      theme_bw() +
      theme(plot.title = element_text(hjust = 0.5,
                                  size = 18),
            plot.subtitle = element_text(hjust = 0.5),
            legend.box.background = element_rect(colour = "black"),
            axis.text.x = element_text(size = 7),
            axis.text.y = element_text(size = 12),
            axis.title = element_text(size = 16),
            legend.title = element_text(size = 13,
                                        hjust = 0.5),
            legend.text = element_text(size = 10,
                                       hjust = 0.5),
            strip.text.x = element_text(size = 14)) 
      
  }, height = 400, width = 800)
  output$pdfview <- renderTable({
    req(input$file_input)
    meta_df <- meta_function(input$file_input$datapath)
    meta_df <- meta_df |> rename(Course_Number = 'course_num',
                                 Subject = 'subject',
                                 Semester = 'semester',
                                 Year = 'year',
                                 Control_Number = 'control_num',
                                 Total_Evals = 'n_evals',
                                 Total_Evals_University = 'n_evals_univ')
    return(meta_df)
  })
  output$pdf_display <- renderTable({
    req(input$file_input)
    pdf_df <- pdf_function_full(input$file_input$datapath)
    pdf_df <- pdf_df |> filter(responses_hm != "Too High" &
                        responses_hm != "Too Low" &
                        responses_hm != "Appropriate" &
                        responses_hm != "Somewhat High" &
                        responses_hm != "Somewhat Low")
    pdf_display <- pdf_df |>
      select(responses, n_students, perc, univ_perc, full_question) |>
      rename(Responses = 'responses',
             Count = 'n_students',
             Percent_of_Students = 'perc',
             University_Percent = 'univ_perc',
             Question = 'full_question')
    return(head(pdf_display))
  })
}
shinyApp(ui, server)
```

add button to select heatmap v bar plot 
```{r}
ui <- fluidPage( 
  titlePanel("Upload File Here"),
  sidebarLayout(
    sidebarPanel(
      fileInput('file_input', 'Upload Student Evaluation
                File (.pdf format only)',
                accept = c('pdf')),
      radioButtons(inputId = "choose_graph", label = "Heatmap or Bar Plot",
                   choices = c("Heatmap", "Bar_Plot")),
      radioButtons(inputId = "choose", label = "Counts or Percent of Students",
                   choices = c("Count", "Percent")),
      ),
    mainPanel(
      plotOutput("heatmap", width = "100%"),
      plotOutput("bar_graph", width = "100%"), 
      uiOutput("pdfview"),
      uiOutput("pdf_display")
    ))
)
server <- function(input, output, session) {
  output$heatmap <- renderPlot({
    req(input$file_input)
    pdf_df <- pdf_function_full(input$file_input$datapath)
    pdf_df <- pdf_df |> filter(responses_hm != "Too High" &
                        responses_hm != "Too Low" &
                        responses_hm != "Appropriate" &
                        responses_hm != "Somewhat High" &
                        responses_hm != "Somewhat Low")
    pdf_df <- pdf_df |> mutate(question_2 = 
                       fct_relevel(full_question, c("Valuable",
                                               "Organized",
                                               "Learning",
                                               "Fair",
                                               "Timely",
                                               "Constructive",
                                               "Rec_Prof",
                                               "Rec_Course",
                                               "Effective")))
    pdf_df <- pdf_df |> mutate(perc = as.double(perc))
    pdf_df <- pdf_df |> rename(Count = 'count_hm',
                               Percent = 'perc')
    meta_df <- meta_function(input$file_input$datapath)
    title <- paste(meta_df[1, 2], meta_df[1, 1], sep = " ", collapse = NULL)
    subtitle <- paste(meta_df[1, 3], meta_df[1, 4], sep = " ", collapse = NULL)
    ggplot(data = pdf_df, aes(x = responses_hm, y = fct_rev(question_2),
                                fill = .data[[input$choose]])) +
    geom_tile() +
    scale_fill_viridis_c(direction = 1) +
      labs(x = "Responses",
           y = "Questions",
           fill = input$choose,
           title = title,
           subtitle = subtitle) +
      geom_text(aes(label = .data[[input$choose]],
                  fontface = 'bold',
                  size = 20),
            show.legend = FALSE) +
      theme_bw() +
      theme(plot.title = element_text(hjust = 0.5,
                                  size = 18),
            plot.subtitle = element_text(hjust = 0.5),
            legend.box.background = element_rect(colour = "black"),
            axis.text = element_text(size = 14),
            axis.title = element_text(size = 16),
            legend.title = element_text(size = 13,
                                        hjust = 0.5),
            legend.text = element_text(size = 10,
                                       hjust = 0.5)) 
  }, height = 400, width = 900)
  output$bar_graph <- renderPlot({
    req(input$file_input)
    pdf_df <- pdf_function_full(input$file_input$datapath)
    pdf_df <- pdf_df |> filter(responses_hm != "Too High" &
                        responses_hm != "Too Low" &
                        responses_hm != "Appropriate" &
                        responses_hm != "Somewhat High" &
                        responses_hm != "Somewhat Low")
    pdf_df <- pdf_df |> mutate(question_2 = 
                       fct_relevel(full_question, c("Valuable",
                                               "Organized",
                                               "Learning",
                                               "Fair",
                                               "Timely",
                                               "Constructive",
                                               "Rec_Prof",
                                               "Rec_Course",
                                               "Effective")))
    pdf_df <- pdf_df |> mutate(perc = as.double(perc))
    pdf_df <- pdf_df |> rename(Count = 'count_hm',
                               Percent = 'perc')
    meta_df <- meta_function(input$file_input$datapath)
    title <- paste(meta_df[1, 2], meta_df[1, 1], sep = " ", collapse = NULL)
    subtitle <- paste(meta_df[1, 3], meta_df[1, 4], sep = " ", collapse = NULL)
    ggplot(data = pdf_df, aes(x = responses_hm, y = .data[[input$choose]])) +
      geom_col(aes(fill = .data[[input$choose]])) +
      facet_wrap(~question_2) +
      labs(x = "Responses",
           y = input$choose,
           title = title,
           subtitle = subtitle) +
      scale_fill_viridis_c() +
      theme_bw() +
      theme(plot.title = element_text(hjust = 0.5,
                                  size = 18),
            plot.subtitle = element_text(hjust = 0.5),
            legend.box.background = element_rect(colour = "black"),
            axis.text.x = element_text(size = 7),
            axis.text.y = element_text(size = 12),
            axis.title = element_text(size = 16),
            legend.title = element_text(size = 13,
                                        hjust = 0.5),
            legend.text = element_text(size = 10,
                                       hjust = 0.5),
            strip.text.x = element_text(size = 14)) 
      
  }, height = 400, width = 800)
  output$pdfview <- renderTable({
    req(input$file_input)
    meta_df <- meta_function(input$file_input$datapath)
    meta_df <- meta_df |> rename(Course_Number = 'course_num',
                                 Subject = 'subject',
                                 Semester = 'semester',
                                 Year = 'year',
                                 Control_Number = 'control_num',
                                 Total_Evals = 'n_evals',
                                 Total_Evals_University = 'n_evals_univ')
    return(meta_df)
  })
  output$pdf_display <- renderTable({
    req(input$file_input)
    pdf_df <- pdf_function_full(input$file_input$datapath)
    pdf_df <- pdf_df |> filter(responses_hm != "Too High" &
                        responses_hm != "Too Low" &
                        responses_hm != "Appropriate" &
                        responses_hm != "Somewhat High" &
                        responses_hm != "Somewhat Low")
    pdf_display <- pdf_df |>
      select(responses, n_students, perc, univ_perc, full_question) |>
      rename(Responses = 'responses',
             Count = 'n_students',
             Percent_of_Students = 'perc',
             University_Percent = 'univ_perc',
             Question = 'full_question')
    return(head(pdf_display))
  })
}
shinyApp(ui, server)
```

make button work 
```{r}
ui <- fluidPage( 
  titlePanel("Upload File Here"),
  sidebarLayout(
    sidebarPanel(
      fileInput('file_input', 'Upload Student Evaluation
                File (.pdf format only)',
                accept = c('pdf')),
      radioButtons(inputId = "choose_graph", label = "Heatmap or Bar Plot",
                   choices = c("Heatmap", "Bar_Plot")),
      radioButtons(inputId = "choose", label = "Counts or Percent of Students",
                   choices = c("Count", "Percent")),
      ),
    mainPanel(
      plotOutput("choose_plot"),
      uiOutput("pdfview"),
      uiOutput("pdf_display")
    ))
)
server <- function(input, output, session) {
  output$choose_plot <- renderPlot({
    req(input$file_input)
    if (input$choose_graph == "Heatmap") {
      pdf_df <- pdf_function_full(input$file_input$datapath)
    pdf_df <- pdf_df |> filter(responses_hm != "Too High" &
                        responses_hm != "Too Low" &
                        responses_hm != "Appropriate" &
                        responses_hm != "Somewhat High" &
                        responses_hm != "Somewhat Low")
    pdf_df <- pdf_df |> mutate(question_2 = 
                       fct_relevel(full_question, c("Valuable",
                                               "Organized",
                                               "Learning",
                                               "Fair",
                                               "Timely",
                                               "Constructive",
                                               "Rec_Prof",
                                               "Rec_Course",
                                               "Effective")))
    pdf_df <- pdf_df |> mutate(perc = as.double(perc))
    pdf_df <- pdf_df |> rename(Count = 'count_hm',
                               Percent = 'perc')
    meta_df <- meta_function(input$file_input$datapath)
    title <- paste(meta_df[1, 2], meta_df[1, 1], sep = " ", collapse = NULL)
    subtitle <- paste(meta_df[1, 3], meta_df[1, 4], sep = " ", collapse = NULL)
    ggplot(data = pdf_df, aes(x = responses_hm, y = fct_rev(question_2),
                                fill = .data[[input$choose]])) +
    geom_tile() +
    scale_fill_viridis_c(direction = 1) +
      labs(x = "Responses",
           y = "Questions",
           fill = input$choose,
           title = title,
           subtitle = subtitle) +
      geom_text(aes(label = .data[[input$choose]],
                  fontface = 'bold',
                  size = 20),
            show.legend = FALSE) +
      theme_bw() +
      theme(plot.title = element_text(hjust = 0.5,
                                  size = 18),
            plot.subtitle = element_text(hjust = 0.5),
            legend.box.background = element_rect(colour = "black"),
            axis.text = element_text(size = 14),
            axis.title = element_text(size = 16),
            legend.title = element_text(size = 13,
                                        hjust = 0.5),
            legend.text = element_text(size = 10,
                                       hjust = 0.5)) 
    } else{
      pdf_df <- pdf_function_full(input$file_input$datapath)
    pdf_df <- pdf_df |> filter(responses_hm != "Too High" &
                        responses_hm != "Too Low" &
                        responses_hm != "Appropriate" &
                        responses_hm != "Somewhat High" &
                        responses_hm != "Somewhat Low")
    pdf_df <- pdf_df |> mutate(question_2 = 
                       fct_relevel(full_question, c("Valuable",
                                               "Organized",
                                               "Learning",
                                               "Fair",
                                               "Timely",
                                               "Constructive",
                                               "Rec_Prof",
                                               "Rec_Course",
                                               "Effective")))
    pdf_df <- pdf_df |> mutate(perc = as.double(perc))
    pdf_df <- pdf_df |> rename(Count = 'count_hm',
                               Percent = 'perc')
    meta_df <- meta_function(input$file_input$datapath)
    title <- paste(meta_df[1, 2], meta_df[1, 1], sep = " ", collapse = NULL)
    subtitle <- paste(meta_df[1, 3], meta_df[1, 4], sep = " ", collapse = NULL)
    ggplot(data = pdf_df, aes(x = responses_hm, y = .data[[input$choose]])) +
      geom_col(aes(fill = .data[[input$choose]])) +
      facet_wrap(~question_2) +
      labs(x = "Responses",
           y = input$choose,
           title = title,
           subtitle = subtitle) +
      scale_fill_viridis_c() +
      theme_bw() +
      theme(plot.title = element_text(hjust = 0.5,
                                  size = 18),
            plot.subtitle = element_text(hjust = 0.5),
            legend.box.background = element_rect(colour = "black"),
            axis.text.x = element_text(size = 7),
            axis.text.y = element_text(size = 12),
            axis.title = element_text(size = 16),
            legend.title = element_text(size = 13,
                                        hjust = 0.5),
            legend.text = element_text(size = 10,
                                       hjust = 0.5),
            strip.text.x = element_text(size = 14)) 
    }
  })
  output$pdfview <- renderTable({
    req(input$file_input)
    meta_df <- meta_function(input$file_input$datapath)
    meta_df <- meta_df |> rename(Course_Number = 'course_num',
                                 Subject = 'subject',
                                 Semester = 'semester',
                                 Year = 'year',
                                 Control_Number = 'control_num',
                                 Total_Evals = 'n_evals',
                                 Total_Evals_University = 'n_evals_univ')
    return(meta_df)
  })
  output$pdf_display <- renderTable({
    req(input$file_input)
    pdf_df <- pdf_function_full(input$file_input$datapath)
    pdf_df <- pdf_df |> filter(responses_hm != "Too High" &
                        responses_hm != "Too Low" &
                        responses_hm != "Appropriate" &
                        responses_hm != "Somewhat High" &
                        responses_hm != "Somewhat Low")
    pdf_display <- pdf_df |>
      select(responses, n_students, perc, univ_perc, full_question) |>
      rename(Responses = 'responses',
             Count = 'n_students',
             Percent_of_Students = 'perc',
             University_Percent = 'univ_perc',
             Question = 'full_question')
    return(head(pdf_display))
  })
}
shinyApp(ui, server)
```

question numbers added/change label color 
```{r}
ui <- fluidPage( 
  titlePanel("Upload File Here"),
  sidebarLayout(
    sidebarPanel(
      fileInput('file_input', 'Upload Student Evaluation
                File (.pdf format only)',
                accept = c('pdf')),
      radioButtons(inputId = "choose_graph", label = "Heatmap or Bar Plot",
                   choices = c("Heatmap", "Bar Plot")),
      radioButtons(inputId = "choose", label = "Counts or Percent of Students",
                   choices = c("Count", "Percent")),
      ),
    mainPanel(
      plotOutput("choose_plot"),
      uiOutput("pdfview"),
      uiOutput("pdf_display")
    ))
)
server <- function(input, output, session) {
  output$choose_plot <- renderPlot({
    req(input$file_input)
    if (input$choose_graph == "Heatmap") {
      pdf_df <- pdf_function_full(input$file_input$datapath)
    pdf_df <- pdf_df |> filter(responses_hm != "Too High" &
                        responses_hm != "Too Low" &
                        responses_hm != "Appropriate" &
                        responses_hm != "Somewhat High" &
                        responses_hm != "Somewhat Low")
    pdf_df <- pdf_df |> mutate(question_2 = 
                       fct_relevel(full_question, c("Q1. Valuable",
                                               "Q2. Organized",
                                               "Q3. Learning",
                                               "Q5a. Fair",
                                               "Q5b. Timely",
                                               "Q5c. Constructive",
                                               "Q6a. Rec_Prof",
                                               "Q6b. Rec_Course",
                                               "Q6c. Effective")))
    pdf_df <- pdf_df |> mutate(perc = as.double(perc))
    pdf_df <- pdf_df |> rename(Count = 'count_hm',
                               Percent = 'perc')
    meta_df <- meta_function(input$file_input$datapath)
    title <- paste(meta_df[1, 2], meta_df[1, 1], sep = " ", collapse = NULL)
    subtitle <- paste(meta_df[1, 3], meta_df[1, 4], sep = " ", collapse = NULL)
    ggplot(data = pdf_df, aes(x = responses_hm, y = fct_rev(question_2),
                                fill = .data[[input$choose]])) +
    geom_tile() +
    scale_fill_viridis_c(direction = 1) +
      labs(x = "Responses",
           y = "Questions",
           fill = input$choose,
           title = title,
           subtitle = subtitle) +
      geom_text(aes(label = .data[[input$choose]],
                  fontface = 'bold'), size = 6,
                colour = "gray",
            show.legend = FALSE) +
      theme_bw() +
      theme(plot.title = element_text(hjust = 0.5,
                                  size = 18),
            plot.subtitle = element_text(hjust = 0.5),
            legend.box.background = element_rect(colour = "black"),
            axis.text = element_text(size = 14),
            axis.title = element_text(size = 16),
            legend.title = element_text(size = 13,
                                        hjust = 0.5),
            legend.text = element_text(size = 10,
                                       hjust = 0.5)) 
    } else{
      pdf_df <- pdf_function_full(input$file_input$datapath)
    pdf_df <- pdf_df |> filter(responses_hm != "Too High" &
                        responses_hm != "Too Low" &
                        responses_hm != "Appropriate" &
                        responses_hm != "Somewhat High" &
                        responses_hm != "Somewhat Low")
    pdf_df <- pdf_df |> mutate(question_2 = 
                       fct_relevel(full_question, c("Q1. Valuable",
                                               "Q2. Organized",
                                               "Q3. Learning",
                                               "Q5a. Fair",
                                               "Q5b. Timely",
                                               "Q5c. Constructive",
                                               "Q6a. Rec_Prof",
                                               "Q6b. Rec_Course",
                                               "Q6c. Effective")))
    pdf_df <- pdf_df |> mutate(perc = as.double(perc))
    pdf_df <- pdf_df |> rename(Count = 'count_hm',
                               Percent = 'perc')
    meta_df <- meta_function(input$file_input$datapath)
    title <- paste(meta_df[1, 2], meta_df[1, 1], sep = " ", collapse = NULL)
    subtitle <- paste(meta_df[1, 3], meta_df[1, 4], sep = " ", collapse = NULL)
    ggplot(data = pdf_df, aes(x = responses_hm, y = .data[[input$choose]])) +
      geom_col(aes(fill = .data[[input$choose]])) +
      facet_wrap(~question_2) +
      labs(x = "Responses",
           y = input$choose,
           title = title,
           subtitle = subtitle) +
      scale_fill_viridis_c() +
      theme_bw() +
      theme(plot.title = element_text(hjust = 0.5,
                                  size = 18),
            plot.subtitle = element_text(hjust = 0.5),
            legend.box.background = element_rect(colour = "black"),
            axis.text.x = element_text(size = 7),
            axis.text.y = element_text(size = 12),
            axis.title = element_text(size = 16),
            legend.title = element_text(size = 13,
                                        hjust = 0.5),
            legend.text = element_text(size = 10,
                                       hjust = 0.5),
            strip.text.x = element_text(size = 14)) 
    }
  })
  output$pdfview <- renderTable({
    req(input$file_input)
    meta_df <- meta_function(input$file_input$datapath)
    meta_df <- meta_df |> rename(Course_Number = 'course_num',
                                 Subject = 'subject',
                                 Semester = 'semester',
                                 Year = 'year',
                                 Control_Number = 'control_num',
                                 Total_Evals = 'n_evals',
                                 Total_Evals_University = 'n_evals_univ')
    return(meta_df)
  })
  output$pdf_display <- renderTable({
    req(input$file_input)
    pdf_df <- pdf_function_full(input$file_input$datapath)
    pdf_df <- pdf_df |> filter(responses_hm != "Too High" &
                        responses_hm != "Too Low" &
                        responses_hm != "Appropriate" &
                        responses_hm != "Somewhat High" &
                        responses_hm != "Somewhat Low")
    pdf_display <- pdf_df |>
      select(responses, n_students, perc, univ_perc, full_question) |>
      rename(Responses = 'responses',
             Count = 'n_students',
             Percent_of_Students = 'perc',
             University_Percent = 'univ_perc',
             Question = 'full_question')
    return(head(pdf_display))
  })
}
shinyApp(ui, server)
```

edit output table to show each question
```{r}
ui <- fluidPage( 
  titlePanel("Upload File Here"),
  sidebarLayout(
    sidebarPanel(
      fileInput('file_input', 'Upload Student Evaluation
                File (.pdf format only)',
                accept = c('pdf')),
      radioButtons(inputId = "choose_graph", label = "Heatmap or Bar Plot",
                   choices = c("Heatmap", "Bar Plot")),
      radioButtons(inputId = "choose", label = "Counts or Percent of Students",
                   choices = c("Count", "Percent")),
      ),
    mainPanel(
      plotOutput("choose_plot"),
      uiOutput("pdfview"),
      uiOutput("pdf_display")
    ))
)
server <- function(input, output, session) {
  output$choose_plot <- renderPlot({
    req(input$file_input)
    if (input$choose_graph == "Heatmap") {
      pdf_df <- pdf_function_full(input$file_input$datapath)
    pdf_df <- pdf_df |> filter(responses_hm != "Too High" &
                        responses_hm != "Too Low" &
                        responses_hm != "Appropriate" &
                        responses_hm != "Somewhat High" &
                        responses_hm != "Somewhat Low")
    pdf_df <- pdf_df |> mutate(question_2 = 
                       fct_relevel(full_question, c("Q1. Valuable",
                                               "Q2. Organized",
                                               "Q3. Learning",
                                               "Q5a. Fair",
                                               "Q5b. Timely",
                                               "Q5c. Constructive",
                                               "Q6a. Rec_Prof",
                                               "Q6b. Rec_Course",
                                               "Q6c. Effective")))
    pdf_df <- pdf_df |> mutate(perc = as.double(perc))
    pdf_df <- pdf_df |> rename(Count = 'count_hm',
                               Percent = 'perc')
    meta_df <- meta_function(input$file_input$datapath)
    title <- paste(meta_df[1, 2], meta_df[1, 1], sep = " ", collapse = NULL)
    subtitle <- paste(meta_df[1, 3], meta_df[1, 4], sep = " ", collapse = NULL)
    ggplot(data = pdf_df, aes(x = responses_hm, y = fct_rev(question_2),
                                fill = .data[[input$choose]])) +
    geom_tile() +
    scale_fill_viridis_c(direction = 1) +
      labs(x = "Responses",
           y = "Questions",
           fill = input$choose,
           title = title,
           subtitle = subtitle) +
      geom_text(aes(label = .data[[input$choose]],
                  fontface = 'bold'), size = 6,
                colour = "gray",
            show.legend = FALSE) +
      theme_bw() +
      theme(plot.title = element_text(hjust = 0.5,
                                  size = 18),
            plot.subtitle = element_text(hjust = 0.5),
            legend.box.background = element_rect(colour = "black"),
            axis.text = element_text(size = 14),
            axis.title = element_text(size = 16),
            legend.title = element_text(size = 13,
                                        hjust = 0.5),
            legend.text = element_text(size = 10,
                                       hjust = 0.5)) 
    } else{
      pdf_df <- pdf_function_full(input$file_input$datapath)
    pdf_df <- pdf_df |> filter(responses_hm != "Too High" &
                        responses_hm != "Too Low" &
                        responses_hm != "Appropriate" &
                        responses_hm != "Somewhat High" &
                        responses_hm != "Somewhat Low")
    pdf_df <- pdf_df |> mutate(question_2 = 
                       fct_relevel(full_question, c("Q1. Valuable",
                                               "Q2. Organized",
                                               "Q3. Learning",
                                               "Q5a. Fair",
                                               "Q5b. Timely",
                                               "Q5c. Constructive",
                                               "Q6a. Rec_Prof",
                                               "Q6b. Rec_Course",
                                               "Q6c. Effective")))
    pdf_df <- pdf_df |> mutate(perc = as.double(perc))
    pdf_df <- pdf_df |> rename(Count = 'count_hm',
                               Percent = 'perc')
    meta_df <- meta_function(input$file_input$datapath)
    title <- paste(meta_df[1, 2], meta_df[1, 1], sep = " ", collapse = NULL)
    subtitle <- paste(meta_df[1, 3], meta_df[1, 4], sep = " ", collapse = NULL)
    ggplot(data = pdf_df, aes(x = responses_hm, y = .data[[input$choose]])) +
      geom_col(aes(fill = .data[[input$choose]])) +
      facet_wrap(~question_2) +
      labs(x = "Responses",
           y = input$choose,
           title = title,
           subtitle = subtitle) +
      scale_fill_viridis_c() +
      theme_bw() +
      theme(plot.title = element_text(hjust = 0.5,
                                  size = 18),
            plot.subtitle = element_text(hjust = 0.5),
            legend.box.background = element_rect(colour = "black"),
            axis.text.x = element_text(size = 7),
            axis.text.y = element_text(size = 12),
            axis.title = element_text(size = 16),
            legend.title = element_text(size = 13,
                                        hjust = 0.5),
            legend.text = element_text(size = 10,
                                       hjust = 0.5),
            strip.text.x = element_text(size = 14)) 
    }
  })
  output$pdfview <- renderTable({
    req(input$file_input)
    meta_df <- meta_function(input$file_input$datapath)
    meta_df <- meta_df |> rename(Course_Number = 'course_num',
                                 Subject = 'subject',
                                 Semester = 'semester',
                                 Year = 'year',
                                 Control_Number = 'control_num',
                                 Total_Evals = 'n_evals',
                                 Total_Evals_University = 'n_evals_univ')
    return(meta_df)
  })
  output$pdf_display <- renderTable({
    req(input$file_input)
    pdf_df <- pdf_function_full(input$file_input$datapath)
    pdf_df <- pdf_df |> filter(responses_hm != "Too High" &
                        responses_hm != "Too Low" &
                        responses_hm != "Appropriate" &
                        responses_hm != "Somewhat High" &
                        responses_hm != "Somewhat Low")
    pdf_display <- pdf_df |>
      select(responses, n_students, perc, univ_perc, full_question) |>
      rename(Responses = 'responses',
             Count = 'n_students',
             Percent_of_Students = 'perc',
             University_Percent = 'univ_perc',
             Question = 'full_question')
    pdf_display <- pdf_display |> filter(Responses == "Strongly Agree" |
                                           Responses == "Agree")
    return(head(pdf_display))
  })
}
shinyApp(ui, server)
```

trying to make things look better 
```{r}
ui <- fluidPage( 
  titlePanel("Upload File Here"),
  sidebarLayout(
    sidebarPanel(
      fileInput('file_input', 'Upload Student Evaluation
                File (.pdf format only)',
                accept = c('pdf')),
      radioButtons(inputId = "choose_graph", label = "Heatmap or Bar Plot",
                   choices = c("Heatmap", "Bar Plot")),
      radioButtons(inputId = "choose", label = "Counts or Percent of Students",
                   choices = c("Count", "Percent")),
      ),
    mainPanel(
      plotOutput("choose_plot", width = "100%"),
      tableOutput("pdfview"),
      tableOutput("pdf_display")
    ))
)
server <- function(input, output, session) {
  output$choose_plot <- renderPlot({
    req(input$file_input)
    if (input$choose_graph == "Heatmap") {
      pdf_df <- pdf_function_full(input$file_input$datapath)
    pdf_df <- pdf_df |> filter(responses_hm != "Too High" &
                        responses_hm != "Too Low" &
                        responses_hm != "Appropriate" &
                        responses_hm != "Somewhat High" &
                        responses_hm != "Somewhat Low")
    pdf_df <- pdf_df |> mutate(question_2 = 
                       fct_relevel(full_question, c("Q1. Valuable",
                                               "Q2. Organized",
                                               "Q3. Learning",
                                               "Q5a. Fair",
                                               "Q5b. Timely",
                                               "Q5c. Constructive",
                                               "Q6a. Rec_Prof",
                                               "Q6b. Rec_Course",
                                               "Q6c. Effective")))
    pdf_df <- pdf_df |> mutate(perc = as.double(perc))
    pdf_df <- pdf_df |> rename(Count = 'count_hm',
                               Percent = 'perc')
    meta_df <- meta_function(input$file_input$datapath)
    title <- paste(meta_df[1, 2], meta_df[1, 1], sep = " ", collapse = NULL)
    subtitle <- paste(meta_df[1, 3], meta_df[1, 4], sep = " ", collapse = NULL)
    ggplot(data = pdf_df, aes(x = responses_hm, y = fct_rev(question_2),
                                fill = .data[[input$choose]])) +
    geom_tile() +
    scale_fill_viridis_c(direction = 1) +
      labs(x = "Responses",
           y = "Questions",
           fill = input$choose,
           title = title,
           subtitle = subtitle) +
      geom_shadowtext(aes(label = .data[[input$choose]],
                  fontface = 'bold'), size = 6,
                colour = "gray",
            show.legend = FALSE) +
      theme_bw() +
      theme(plot.title = element_text(hjust = 0.5,
                                  size = 18),
            plot.subtitle = element_text(hjust = 0.5),
            legend.box.background = element_rect(colour = "black"),
            axis.text = element_text(size = 14),
            axis.title = element_text(size = 16),
            legend.title = element_text(size = 13,
                                        hjust = 0.5),
            legend.text = element_text(size = 10,
                                       hjust = 0.5)) 
    } else{
      pdf_df <- pdf_function_full(input$file_input$datapath)
    pdf_df <- pdf_df |> filter(responses_hm != "Too High" &
                        responses_hm != "Too Low" &
                        responses_hm != "Appropriate" &
                        responses_hm != "Somewhat High" &
                        responses_hm != "Somewhat Low")
    pdf_df <- pdf_df |> mutate(question_2 = 
                       fct_relevel(full_question, c("Q1. Valuable",
                                               "Q2. Organized",
                                               "Q3. Learning",
                                               "Q5a. Fair",
                                               "Q5b. Timely",
                                               "Q5c. Constructive",
                                               "Q6a. Rec_Prof",
                                               "Q6b. Rec_Course",
                                               "Q6c. Effective")))
    pdf_df <- pdf_df |> mutate(perc = as.double(perc))
    pdf_df <- pdf_df |> rename(Count = 'count_hm',
                               Percent = 'perc')
    meta_df <- meta_function(input$file_input$datapath)
    title <- paste(meta_df[1, 2], meta_df[1, 1], sep = " ", collapse = NULL)
    subtitle <- paste(meta_df[1, 3], meta_df[1, 4], sep = " ", collapse = NULL)
    ggplot(data = pdf_df, aes(x = responses_hm, y = .data[[input$choose]])) +
      geom_col(aes(fill = .data[[input$choose]])) +
      facet_wrap(~question_2) +
      labs(x = "Responses",
           y = input$choose,
           title = title,
           subtitle = subtitle) +
      scale_fill_viridis_c() +
      theme_bw() +
      theme(plot.title = element_text(hjust = 0.5,
                                  size = 18),
            plot.subtitle = element_text(hjust = 0.5),
            legend.box.background = element_rect(colour = "black"),
            axis.text.x = element_text(size = 5.5,
                                       face = "bold"),
            axis.text.y = element_text(size = 12),
            axis.title = element_text(size = 16),
            legend.title = element_text(size = 13,
                                        hjust = 0.5),
            legend.text = element_text(size = 10,
                                       hjust = 0.5),
            strip.text.x = element_text(size = 14)) 
    }
  }, height = 400, width = 920)
  output$pdfview <- renderTable({
    req(input$file_input)
    meta_df <- meta_function(input$file_input$datapath)
    meta_df <- meta_df |> rename(Course_Number = 'course_num',
                                 Subject = 'subject',
                                 Semester = 'semester',
                                 Year = 'year',
                                 Control_Number = 'control_num',
                                 Total_Evals = 'n_evals',
                                 Total_Evals_University = 'n_evals_univ')
    return(meta_df)
  }, align = 'c')
  output$pdf_display <- renderTable({
    req(input$file_input)
    pdf_df <- pdf_function_full(input$file_input$datapath)
    pdf_df <- pdf_df |> filter(responses_hm != "Too High" &
                        responses_hm != "Too Low" &
                        responses_hm != "Appropriate" &
                        responses_hm != "Somewhat High" &
                        responses_hm != "Somewhat Low")
    pdf_display <- pdf_df |>
      select(responses, n_students, perc, univ_perc, full_question) |>
      rename(Responses = 'responses',
             Count = 'n_students',
             Percent_of_Students = 'perc',
             University_Percent = 'univ_perc',
             Question = 'full_question')
    pdf_display <- pdf_display |> filter(Responses == "Strongly Agree" |
                                           Responses == "Agree")
    return(head(pdf_display))
  }, align = 'l')
}
shinyApp(ui, server)
```

adding navigation bar
```{r}
library(shiny)

ui <- fluidPage(
  navbarPage(title = "Student Evaluation Data",
           tabPanel(title = "Home", 
                    "Upload File"),
           tabPanel(title = "Visualizations",
                    "Choose Plot"),
           tabPanel(title = "Tables",
                    "View Summary Outputs")
          )
)

server <- function(input, output, session) {
  
}

shinyApp(ui, server)
```

step 2
```{r}
ui <- fluidPage(
  navbarPage(title = "Student Evaluation Data",
           tabPanel(title = "Upload and View Visualizations",
                    fluidPage(
                      sidebarLayout(
                        sidebarPanel(
                          fileInput('file_input', 'Upload Student Evaluation Data (.pdf format only)',
                          accept = c('pdf')),
                          ),
                        mainPanel(
                          plotOutput("choose_plot", width = "100%")
                        )
                      )
                    )
                    ),
           # fill content for this tab 
           tabPanel(title = "Tables",
                    "View Summary Outputs")
          )
)
server <- function(input, output, session) {
  
}
shinyApp(ui, server)
```

step 3
```{r}
ui <- fluidPage(
  navbarPage(title = "Student Evaluation Data",
           tabPanel(title = "Upload and View Visualizations",
                    fluidPage(
                      sidebarLayout(
                        sidebarPanel(
                          fileInput('file_input', 'Upload Student Evaluation Data (.pdf format only)',
                          accept = c('pdf')),
                          radioButtons(inputId = "choose_graph", label = "Choose Visualization",
                                       choices = c("Heatmap", "Bar Plot")),
                          ),
                        mainPanel(
                          plotOutput("choose_plot", width = "100%")
                        )
                      )
                    )
                    ),
           # fill content for this tab 
           tabPanel(title = "Tables",
                    "View Summary Outputs")
          )
)
server <- function(input, output, session) {
  
}
shinyApp(ui, server)
```

step 4
```{r}
ui <- fluidPage(
  navbarPage(title = "Student Evaluation Data",
           tabPanel(title = "Upload and View Visualizations",
                    fluidPage(
                      sidebarLayout(
                        sidebarPanel(
                          fileInput('file_input', 'Upload Student Evaluation Data (.pdf format only)',
                          accept = c('pdf')),
                          radioButtons(inputId = "choose_graph", label = "Choose Visualization",
                                       choices = c("Heatmap", "Bar Plot")),
                          radioButtons(inputId = "choose", label = "Counts or Percent of Students",
                                       choices = c("Count", "Percent")),
                          ),
                        mainPanel(
                          plotOutput("choose_plot", width = "100%")
                        )
                      )
                    )
                    ),
           # fill content for this tab 
           tabPanel(title = "Tables",
                    "View Summary Outputs")
          )
)
server <- function(input, output, session) {
  output$choose_plot <- renderPlot({
    req(input$file_input)
    pdf_df <- pdf_function_full(input$file_input$datapath)
    pdf_df <- pdf_df |> filter(responses_hm != "Too High" &
                        responses_hm != "Too Low" &
                        responses_hm != "Appropriate" &
                        responses_hm != "Somewhat High" &
                        responses_hm != "Somewhat Low")
    pdf_df <- pdf_df |> mutate(question_2 = 
                       fct_relevel(full_question, c("Q1. Valuable",
                                               "Q2. Organized",
                                               "Q3. Learning",
                                               "Q5a. Fair",
                                               "Q5b. Timely",
                                               "Q5c. Constructive",
                                               "Q6a. Rec_Prof",
                                               "Q6b. Rec_Course",
                                               "Q6c. Effective")))
    pdf_df <- pdf_df |> mutate(perc = as.double(perc))
    pdf_df <- pdf_df |> rename(Count = 'count_hm',
                               Percent = 'perc')
    meta_df <- meta_function(input$file_input$datapath)
    title <- paste(meta_df[1, 2], meta_df[1, 1], sep = " ", collapse = NULL)
    subtitle <- paste(meta_df[1, 3], meta_df[1, 4], sep = " ", collapse = NULL)
    ggplot(data = pdf_df, aes(x = responses_hm, y = fct_rev(question_2),
                                fill = .data[[input$choose]])) +
    geom_tile() +
    scale_fill_viridis_c(direction = 1) +
      labs(x = "Responses",
           y = "Questions",
           fill = input$choose,
           title = title,
           subtitle = subtitle) +
      geom_shadowtext(aes(label = .data[[input$choose]],
                  fontface = 'bold'), size = 6,
                colour = "gray",
            show.legend = FALSE) +
      theme_bw() +
      theme(plot.title = element_text(hjust = 0.5,
                                  size = 18),
            plot.subtitle = element_text(hjust = 0.5),
            legend.box.background = element_rect(colour = "black"),
            axis.text = element_text(size = 14),
            axis.title = element_text(size = 16),
            legend.title = element_text(size = 13,
                                        hjust = 0.5),
            legend.text = element_text(size = 10,
                                       hjust = 0.5)) 
})
}
shinyApp(ui, server)
```

step 5 
```{r}
ui <- fluidPage(
  navbarPage(title = "Student Evaluation Data",
           tabPanel(title = "Upload and View Visualizations",
                    fluidPage(
                      sidebarLayout(
                        sidebarPanel(
                          fileInput('file_input', 'Upload Student Evaluation Data (.pdf format only)',
                          accept = c('pdf')),
                          radioButtons(inputId = "choose_graph", label = "Choose Visualization",
                                       choices = c("Heatmap", "Bar Plot")),
                          radioButtons(inputId = "choose", label = "Counts or Percent of Students",
                                       choices = c("Count", "Percent")),
                          ),
                        mainPanel(
                          plotOutput("choose_plot", width = "100%")
                        )
                      )
                    )
                    ),
           # fill content for this tab 
           tabPanel(title = "Tables",
                    "View Summary Outputs")
          )
)
server <- function(input, output, session) {
    output$choose_plot <- renderPlot({
    req(input$file_input)
    if (input$choose_graph == "Heatmap") {
    pdf_df <- pdf_function_full(input$file_input$datapath)
    pdf_df <- pdf_df |> filter(responses_hm != "Too High" &
                        responses_hm != "Too Low" &
                        responses_hm != "Appropriate" &
                        responses_hm != "Somewhat High" &
                        responses_hm != "Somewhat Low")
    pdf_df <- pdf_df |> mutate(question_2 = 
                       fct_relevel(full_question, c("Q1. Valuable",
                                               "Q2. Organized",
                                               "Q3. Learning",
                                               "Q5a. Fair",
                                               "Q5b. Timely",
                                               "Q5c. Constructive",
                                               "Q6a. Rec_Prof",
                                               "Q6b. Rec_Course",
                                               "Q6c. Effective")))
    pdf_df <- pdf_df |> mutate(perc = as.double(perc))
    pdf_df <- pdf_df |> rename(Count = 'count_hm',
                               Percent = 'perc')
    meta_df <- meta_function(input$file_input$datapath)
    title <- paste(meta_df[1, 2], meta_df[1, 1], sep = " ", collapse = NULL)
    subtitle <- paste(meta_df[1, 3], meta_df[1, 4], sep = " ", collapse = NULL)
    ggplot(data = pdf_df, aes(x = responses_hm, y = fct_rev(question_2),
                                fill = .data[[input$choose]])) +
    geom_tile() +
    scale_fill_viridis_c(direction = 1) +
      labs(x = "Responses",
           y = "Questions",
           fill = input$choose,
           title = title,
           subtitle = subtitle) +
      geom_shadowtext(aes(label = .data[[input$choose]],
                  fontface = 'bold'), size = 6,
                colour = "gray",
            show.legend = FALSE) +
      theme_bw() +
      theme(plot.title = element_text(hjust = 0.5,
                                  size = 18),
            plot.subtitle = element_text(hjust = 0.5),
            legend.box.background = element_rect(colour = "black"),
            axis.text = element_text(size = 14),
            axis.title = element_text(size = 16),
            legend.title = element_text(size = 13,
                                        hjust = 0.5),
            legend.text = element_text(size = 10,
                                       hjust = 0.5)) 
    } else{
      pdf_df <- pdf_function_full(input$file_input$datapath)
    pdf_df <- pdf_df |> filter(responses_hm != "Too High" &
                        responses_hm != "Too Low" &
                        responses_hm != "Appropriate" &
                        responses_hm != "Somewhat High" &
                        responses_hm != "Somewhat Low")
    pdf_df <- pdf_df |> mutate(question_2 = 
                       fct_relevel(full_question, c("Q1. Valuable",
                                               "Q2. Organized",
                                               "Q3. Learning",
                                               "Q5a. Fair",
                                               "Q5b. Timely",
                                               "Q5c. Constructive",
                                               "Q6a. Rec_Prof",
                                               "Q6b. Rec_Course",
                                               "Q6c. Effective")))
    pdf_df <- pdf_df |> mutate(perc = as.double(perc))
    pdf_df <- pdf_df |> rename(Count = 'count_hm',
                               Percent = 'perc')
    meta_df <- meta_function(input$file_input$datapath)
    title <- paste(meta_df[1, 2], meta_df[1, 1], sep = " ", collapse = NULL)
    subtitle <- paste(meta_df[1, 3], meta_df[1, 4], sep = " ", collapse = NULL)
    ggplot(data = pdf_df, aes(x = responses_hm, y = .data[[input$choose]])) +
      geom_col(aes(fill = .data[[input$choose]])) +
      facet_wrap(~question_2) +
      labs(x = "Responses",
           y = input$choose,
           title = title,
           subtitle = subtitle) +
      scale_fill_viridis_c() +
      theme_bw() +
      theme(plot.title = element_text(hjust = 0.5,
                                  size = 18),
            plot.subtitle = element_text(hjust = 0.5),
            legend.box.background = element_rect(colour = "black"),
            axis.text.x = element_text(size = 5.5,
                                       face = "bold"),
            axis.text.y = element_text(size = 12),
            axis.title = element_text(size = 16),
            legend.title = element_text(size = 13,
                                        hjust = 0.5),
            legend.text = element_text(size = 10,
                                       hjust = 0.5),
            strip.text.x = element_text(size = 14)) 
    }
  }, height = 400, width = 920)
}
shinyApp(ui, server)
```

step 6
```{r}
ui <- fluidPage(
  navbarPage(title = "Student Evaluation Data",
           tabPanel(title = "Upload and View Visualizations",
                    fluidPage(
                      sidebarLayout(
                        sidebarPanel(
                          fileInput('file_input', 'Upload Student Evaluation Data (.pdf format only)',
                          accept = c('pdf')),
                          radioButtons(inputId = "choose_graph", label = "Choose Visualization",
                                       choices = c("Heatmap", "Bar Plot")),
                          radioButtons(inputId = "choose", label = "Counts or Percent of Students",
                                       choices = c("Count", "Percent")),
                          width = 3),
                        mainPanel(
                          plotOutput("choose_plot", width = "100%")
                        )
                      )
                    )
                    ),
           # fill content for this tab 
           tabPanel(title = "Summary Output Tables",
                    tableOutput("pdfview"),
                    tableOutput("pdf_display"))
          )
)
server <- function(input, output, session) {
  output$choose_plot <- renderPlot({
    req(input$file_input)
    if (input$choose_graph == "Heatmap") {
    pdf_df <- pdf_function_full(input$file_input$datapath)
    pdf_df <- pdf_df |> filter(responses_hm != "Too High" &
                        responses_hm != "Too Low" &
                        responses_hm != "Appropriate" &
                        responses_hm != "Somewhat High" &
                        responses_hm != "Somewhat Low")
    pdf_df <- pdf_df |> mutate(question_2 = 
                       fct_relevel(full_question, c("Q1. Valuable",
                                               "Q2. Organized",
                                               "Q3. Learning",
                                               "Q5a. Fair",
                                               "Q5b. Timely",
                                               "Q5c. Constructive",
                                               "Q6a. Rec_Prof",
                                               "Q6b. Rec_Course",
                                               "Q6c. Effective")))
    pdf_df <- pdf_df |> mutate(perc = as.double(perc))
    pdf_df <- pdf_df |> rename(Count = 'count_hm',
                               Percent = 'perc')
    meta_df <- meta_function(input$file_input$datapath)
    title <- paste(meta_df[1, 2], meta_df[1, 1], sep = " ", collapse = NULL)
    subtitle <- paste(meta_df[1, 3], meta_df[1, 4], sep = " ", collapse = NULL)
    ggplot(data = pdf_df, aes(x = responses_hm, y = fct_rev(question_2),
                                fill = .data[[input$choose]])) +
    geom_tile() +
    scale_fill_viridis_c(direction = 1) +
      labs(x = "Responses",
           y = "Questions",
           fill = input$choose,
           title = title,
           subtitle = subtitle) +
      geom_shadowtext(aes(label = .data[[input$choose]],
                  fontface = 'bold'), size = 6,
                colour = "gray",
            show.legend = FALSE) +
      theme_bw() +
      theme(plot.title = element_text(hjust = 0.5,
                                  size = 18),
            plot.subtitle = element_text(hjust = 0.5),
            legend.box.background = element_rect(colour = "black"),
            axis.text = element_text(size = 14),
            axis.title = element_text(size = 16),
            legend.title = element_text(size = 13,
                                        hjust = 0.5),
            legend.text = element_text(size = 10,
                                       hjust = 0.5)) 
    } else{
      pdf_df <- pdf_function_full(input$file_input$datapath)
    pdf_df <- pdf_df |> filter(responses_hm != "Too High" &
                        responses_hm != "Too Low" &
                        responses_hm != "Appropriate" &
                        responses_hm != "Somewhat High" &
                        responses_hm != "Somewhat Low")
    pdf_df <- pdf_df |> mutate(question_2 = 
                       fct_relevel(full_question, c("Q1. Valuable",
                                               "Q2. Organized",
                                               "Q3. Learning",
                                               "Q5a. Fair",
                                               "Q5b. Timely",
                                               "Q5c. Constructive",
                                               "Q6a. Rec_Prof",
                                               "Q6b. Rec_Course",
                                               "Q6c. Effective")))
    pdf_df <- pdf_df |> mutate(responses_barplot =
                                 fct_recode(responses_hm,
                                            AgStrongly = "AgreeStrongly",
                                            A = "Agree",
                                            AgSome = "AgreeSomewhat",
                                            N = "Neutral",
                                            DisSome = "DisagreeSomewhat",
                                            D = "Disagree",
                                            DisStrong = "DisagreeStrongly"))
    pdf_df <- pdf_df |> mutate(perc = as.double(perc))
    pdf_df <- pdf_df |> rename(Count = 'count_hm',
                               Percent = 'perc')
    meta_df <- meta_function(input$file_input$datapath)
    title <- paste(meta_df[1, 2], meta_df[1, 1], sep = " ", collapse = NULL)
    subtitle <- paste(meta_df[1, 3], meta_df[1, 4], sep = " ", collapse = NULL)
    ggplot(data = pdf_df, aes(x = responses_barplot, y = .data[[input$choose]])) +
      geom_col(aes(fill = .data[[input$choose]])) +
      facet_wrap(~question_2) +
      labs(x = "Responses",
           y = input$choose,
           title = title,
           subtitle = subtitle) +
      scale_fill_viridis_c() +
      theme_bw() +
      theme(plot.title = element_text(hjust = 0.5,
                                  size = 18),
            plot.subtitle = element_text(hjust = 0.5),
            legend.box.background = element_rect(colour = "black"),
            axis.text.x = element_text(size = 10),
            axis.text.y = element_text(size = 12),
            axis.title = element_text(size = 16),
            legend.title = element_text(size = 13,
                                        hjust = 0.5),
            legend.text = element_text(size = 10,
                                       hjust = 0.5),
            strip.text.x = element_text(size = 14)) 
    }
  }, height = 550, width = 1050)
  output$pdfview <- renderTable({
    req(input$file_input)
    meta_df <- meta_function(input$file_input$datapath)
    meta_df <- meta_df |> rename(Course_Number = 'course_num',
                                 Subject = 'subject',
                                 Semester = 'semester',
                                 Year = 'year',
                                 Control_Number = 'control_num',
                                 Total_Evals = 'n_evals',
                                 Total_Evals_University = 'n_evals_univ')
    return(meta_df)
  }, align = 'c')
  output$pdf_display <- renderTable({
    req(input$file_input)
    pdf_df <- pdf_function_full(input$file_input$datapath)
    pdf_df <- pdf_df |> filter(responses_hm != "Too High" &
                        responses_hm != "Too Low" &
                        responses_hm != "Appropriate" &
                        responses_hm != "Somewhat High" &
                        responses_hm != "Somewhat Low")
    pdf_display <- pdf_df |>
      select(responses, n_students, perc, univ_perc, full_question) |>
      rename(Responses = 'responses',
             Count = 'n_students',
             Percent_of_Students = 'perc',
             University_Percent = 'univ_perc',
             Question = 'full_question')
    return(head(pdf_display))
  }, align = 'l')
}
shinyApp(ui, server)
```

adding more
```{r}
ui <- fluidPage(
  navbarPage(title = "Student Evaluation Data",
           tabPanel(title = "Upload and View Visualizations",
                    fluidPage(
                      sidebarLayout(
                        sidebarPanel(
                          fileInput('file_input', 'Upload Student Evaluation Data (.pdf format only)',
                          accept = c('pdf')),
                          radioButtons(inputId = "choose_graph", label = "Choose Visualization",
                                       choices = c("Heatmap", "Bar Plot")),
                          radioButtons(inputId = "choose", label = "Counts or Percent of Students",
                                       choices = c("Count", "Percent")),
                          width = 3),
                        mainPanel(
                          plotOutput("choose_plot", width = "100%")
                        )
                      )
                    )
                    ),
           # fill content for this tab 
           tabPanel(title = "Summary Output Tables",
                    tableOutput("pdfview"),
                    tableOutput("pdf_display"))
          )
)
server <- function(input, output, session) {
  output$choose_plot <- renderPlot({
    req(input$file_input)
    if (input$choose_graph == "Heatmap") {
    pdf_df <- pdf_function_full(input$file_input$datapath)
    pdf_df <- pdf_df |> filter(responses_hm != "Too High" &
                        responses_hm != "Too Low" &
                        responses_hm != "Appropriate" &
                        responses_hm != "Somewhat High" &
                        responses_hm != "Somewhat Low")
    pdf_df <- pdf_df |> mutate(question_2 = 
                       fct_relevel(full_question, c("Q1. Valuable",
                                               "Q2. Organized",
                                               "Q3. Learning",
                                               "Q5a. Fair",
                                               "Q5b. Timely",
                                               "Q5c. Constructive",
                                               "Q6a. Rec_Prof",
                                               "Q6b. Rec_Course",
                                               "Q6c. Effective")))
    pdf_df <- pdf_df |> mutate(perc = as.double(perc))
    pdf_df <- pdf_df |> rename(Count = 'count_hm',
                               Percent = 'perc')
    meta_df <- meta_function(input$file_input$datapath)
    title <- paste(meta_df[1, 2], meta_df[1, 1], sep = " ", collapse = NULL)
    subtitle <- paste(meta_df[1, 3], meta_df[1, 4], sep = " ", collapse = NULL)
    ggplot(data = pdf_df, aes(x = responses_hm, y = fct_rev(question_2),
                                fill = .data[[input$choose]])) +
    geom_tile() +
    scale_fill_viridis_c(direction = 1) +
      labs(x = "Responses",
           y = "Questions",
           fill = input$choose,
           title = title,
           subtitle = subtitle) +
      geom_shadowtext(aes(label = .data[[input$choose]],
                  fontface = 'bold'), size = 6,
                colour = "gray",
            show.legend = FALSE) +
      theme_bw() +
      theme(plot.title = element_text(hjust = 0.5,
                                  size = 18),
            plot.subtitle = element_text(hjust = 0.5),
            legend.box.background = element_rect(colour = "black"),
            axis.text = element_text(size = 14),
            axis.title = element_text(size = 16),
            legend.title = element_text(size = 13,
                                        hjust = 0.5),
            legend.text = element_text(size = 10,
                                       hjust = 0.5)) 
    } else{
      pdf_df <- pdf_function_full(input$file_input$datapath)
    pdf_df <- pdf_df |> filter(responses_hm != "Too High" &
                        responses_hm != "Too Low" &
                        responses_hm != "Appropriate" &
                        responses_hm != "Somewhat High" &
                        responses_hm != "Somewhat Low")
    pdf_df <- pdf_df |> mutate(question_2 = 
                       fct_relevel(full_question, c("Q1. Valuable",
                                               "Q2. Organized",
                                               "Q3. Learning",
                                               "Q5a. Fair",
                                               "Q5b. Timely",
                                               "Q5c. Constructive",
                                               "Q6a. Rec_Prof",
                                               "Q6b. Rec_Course",
                                               "Q6c. Effective")))
    pdf_df <- pdf_df |> mutate(responses_barplot =
                                 fct_recode(responses_hm,
                                            AgStrongly = "AgreeStrongly",
                                            A = "Agree",
                                            AgSome = "AgreeSomewhat",
                                            N = "Neutral",
                                            DisSome = "DisagreeSomewhat",
                                            D = "Disagree",
                                            DisStrong = "DisagreeStrongly"))
    pdf_df <- pdf_df |> mutate(perc = as.double(perc))
    pdf_df <- pdf_df |> rename(Count = 'count_hm',
                               Percent = 'perc')
    meta_df <- meta_function(input$file_input$datapath)
    title <- paste(meta_df[1, 2], meta_df[1, 1], sep = " ", collapse = NULL)
    subtitle <- paste(meta_df[1, 3], meta_df[1, 4], sep = " ", collapse = NULL)
    ggplot(data = pdf_df, aes(x = responses_barplot, y = .data[[input$choose]])) +
      geom_col(aes(fill = .data[[input$choose]])) +
      facet_wrap(~question_2) +
      labs(x = "Responses",
           y = input$choose,
           title = title,
           subtitle = subtitle) +
      scale_fill_viridis_c() +
      theme_bw() +
      theme(plot.title = element_text(hjust = 0.5,
                                  size = 18),
            plot.subtitle = element_text(hjust = 0.5),
            legend.box.background = element_rect(colour = "black"),
            axis.text.x = element_text(size = 10),
            axis.text.y = element_text(size = 12),
            axis.title = element_text(size = 16),
            legend.title = element_text(size = 13,
                                        hjust = 0.5),
            legend.text = element_text(size = 10,
                                       hjust = 0.5),
            strip.text.x = element_text(size = 14)) 
    }
  }, height = 550, width = 1050)
  output$pdfview <- renderTable({
    req(input$file_input)
    meta_df <- meta_function(input$file_input$datapath)
    meta_df <- meta_df |> rename(Course_Number = 'course_num',
                                 Subject = 'subject',
                                 Semester = 'semester',
                                 Year = 'year',
                                 Control_Number = 'control_num',
                                 Total_Evals = 'n_evals',
                                 Total_Evals_University = 'n_evals_univ')
    return(meta_df)
  }, align = 'c')
  output$pdf_display <- renderTable({
    req(input$file_input)
    pdf_df <- pdf_function_full(input$file_input$datapath)
    pdf_df <- pdf_df |> filter(responses_hm != "Too High" &
                        responses_hm != "Too Low" &
                        responses_hm != "Appropriate" &
                        responses_hm != "Somewhat High" &
                        responses_hm != "Somewhat Low")
    pdf_display <- pdf_df |>
      select(responses, n_students, perc, univ_perc, full_question) |>
      rename(Responses = 'responses',
             Count = 'n_students',
             Percent_of_Students = 'perc',
             University_Percent = 'univ_perc',
             Question = 'full_question')
    return(head(pdf_display))
  }, align = 'l')
}
shinyApp(ui, server)
```

